\documentclass{../armymemo}

\author{John Doe}\rank{CPT}\branch{CY}\title{COMMANDING}
\officesymbol{ABC-DEF-GH}
\signaturedate{10 April 2019}
\memoline{MEMORANDUM FOR U.S. Army Command and General Staff College (ATZL), 100 Stimson Avenue, Ft Leavenworth, KS 66027-1352}
\subject{Using and Preparing a Memorandum with \LaTeX}
\documentmark{UNCLASSIFIED//FOR OFFICIAL USE ONLY (EXAMPLE ONLY)}
\suspensedate{1 JAN 2019}
\authority{AUTHORITY LINE}
\addencl{AR 25-50}
% \addencl{Resume}
% \addencl{Things}
\adddistro{DISTRO 1}
\adddistro{DISTRO 2}
\adddistro{DISTRO 3}
\addcf{CF 1}
\addcf{CF 2}

\begin{document}

\begin{enumerate}
\item See paragraph 2-2 (of AR 25-50) for when to use a memorandum.
\item Single space the text and double space between paragraphs and subparagraphs. Insert two blank spaces after ending punctuation (period and question mark). Insert two blank spaces after a colon. When numbering subparagraphs, insert two blank spaces after parentheses.
\item When a memorandum has more than one paragraph, number the paragraphs consecutively. When paragraphs are subdivided, designate first subdivisions using lowercase letters of the alphabet and indent 1/4 inch as shown below.
  \begin{enumerate}
  \item When a paragraph is subdivided, it must have at least two subparagraphs.
  \item If there is a subparagraph ``a,'' there must be a subparagraph ``b.''
    \begin{enumerate}
    \item Designate second subdivisions by numbers in parentheses; for example (1), (2), and (3) and indent by 1/2 inch as shown.
    \item Do not subdivide beyond the third subdivision.
      \begin{enumerate}
      \item Do not indent any further than the second subdivision.
      \item Use (a), (b), (c), and so forth at this level.
      \end{enumerate}
    \end{enumerate}
  \end{enumerate}
\item Moby Dick, a classic American Novel, the text of which is public domain,
  follows in several paragraphs to make a longer example:

  \begin{enumerate}
  \item Call me Ishmael. Some years ago- never mind how long precisely- having little or
    no money in my purse, and nothing particular to interest me on shore, I thought
    I would sail about a little and see the watery part of the world. It is a way I
    have of driving off the spleen and regulating the circulation. Whenever I find
    myself growing grim about the mouth; whenever it is a damp, drizzly November in
    my soul; whenever I find myself involuntarily pausing before coffin warehouses,
    and bringing up the rear of every funeral I meet; and especially whenever my
    hypos get such an upper hand of me, that it requires a strong moral principle to
    prevent me from deliberately stepping into the street, and methodically knocking
    people's hats off- then, I account it high time to get to sea as soon as I can.
    This is my substitute for pistol and ball. With a philosophical flourish Cato
    throws himself upon his sword; I quietly take to the ship. There is nothing
    surprising in this. If they but knew it, almost all men in their degree, some
    time or other, cherish very nearly the same feelings towards the ocean with me.

  \item There now is your insular city of the Manhattoes, belted round by wharves as
    Indian isles by coral reefs- commerce surrounds it with her surf. Right and
    left, the streets take you waterward. Its extreme downtown is the battery, where
    that noble mole is washed by waves, and cooled by breezes, which a few hours
    previous were out of sight of land. Look at the crowds of water-gazers there.

  \item Circumambulate the city of a dreamy Sabbath afternoon. Go from Corlears Hook to
    Coenties Slip, and from thence, by Whitehall, northward. What do you see?-
    Posted like silent sentinels all around the town, stand thousands upon thousands
    of mortal men fixed in ocean reveries. Some leaning against the spiles; some
    seated upon the pier-heads; some looking over the bulwarks of ships from China;
    some high aloft in the rigging, as if striving to get a still better seaward
    peep. But these are all landsmen; of week days pent up in lath and plaster- tied
    to counters, nailed to benches, clinched to desks. How then is this? Are the
    green fields gone? What do they here?

  \item But look! here come more crowds, pacing straight for the water, and seemingly
    bound for a dive. Strange! Nothing will content them but the extremest limit of
    the land; loitering under the shady lee of yonder warehouses will not suffice.
    No. They must get just as nigh the water as they possibly can without falling
    And there they stand- miles of them- leagues. Inlanders all, they come from
    lanes and alleys, streets avenues- north, east, south, and west. Yet here they
    all unite. Tell me, does the magnetic virtue of the needles of the compasses of
    all those ships attract them thither?

  \item Once more. Say you are in the country; in some high land of lakes. Take almost
    any path you please, and ten to one it carries you down in a dale, and leaves
    you there by a pool in the stream. There is magic in it. Let the most
    absent-minded of men be plunged in his deepest reveries- stand that man on his
    legs, set his feet a-going, and he will infallibly lead you to water, if water
    there be in all that region. Should you ever be athirst in the great American
    desert, try this experiment, if your caravan happen to be supplied with a
    metaphysical professor. Yes, as every one knows, meditation and water are wedded
    for ever.

  \end{enumerate}

\item POC for this memo is John Doe, who can be reached at \texttt{john@dev.null}
  or (555) 555-1234.

\end{enumerate}


\end{document}

